---
title: "Dissertation: Chapter 2"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author:
- Joshua Martin (adapted from code from Kevin Tang)
output:
  html_document:
    theme: default
    toc: yes
  pdf_document:
    highlight: zenburn
    toc: yes
editor_options: 
  chunk_output_type: console
---

Loading in the data


```{r}
rm(list=ls())
df = read.csv('/Users/joshmartin/Dropbox (UFL)/dissertation/dissertation_pipelines/2_ASR_analysis/step2-13_check_for_correctness_manually_csvs/done_manualCorrectness.csv', header=TRUE)

str(df)
```

Load the libraries

```{r}
library(lme4)
library(sjPlot)
library(ggplot2)
library(lmerTest)
library(brms)

z.fun <- function(df,variables) { 
  for (variable in variables) {
  df[paste0(variable,'.z')] <- NULL
  df[paste0(variable,'.z')] <- as.numeric(scale(df[variable]))
  }
  return (df)
}
log10.lpc.z.fun <- function(df,variables) { 
  for (variable in variables) {
  df[paste0(variable,'.log10.lpc.z')] <- NULL
  df[paste0(variable,'.log10.lpc.z')] <- as.numeric(scale(log10(df[variable]+1)))
  }
  return (df)
}

```

Examine some variables

```{r}
# Examine how many features per speaker and its distribution
plot(table(df$Speaker))
plot(density(table(df$Speaker)))

table(df$Completive)

table(df$Speaker,df$Completive)


# Speech rate
plot(density(df$SpeechRate))

# Speech to Noise Ratio
plot(df$WadaSNRRigal)

# Correctness
table(df$amazon_transcription_cleaned_correctness)
table(df$deepspeech_transcription_cleaned_correctness)
table(df$google_transcription_cleaned_correctness)
table(df$IBMWatson_transcription_cleaned_correctness)
table(df$microsoft_transcription_cleaned_correctness)


# Correctness by feature
table(df$amazon_transcription_cleaned_correctness, df$Completive)
table(df$deepspeech_transcription_cleaned_correctness, df$Completive)
table(df$google_transcription_cleaned_correctness, df$Completive)
table(df$IBMWatson_transcription_cleaned_correctness, df$Completive)
table(df$microsoft_transcription_cleaned_correctness, df$Completive)


# pre-feature and post-feature WER
plot(df$amazon_transcription_cleaned_preFeature_WER)
plot(df$amazon_transcription_cleaned_postFeature_WER)
plot(df$deepspeech_transcription_cleaned_preFeature_WER)
plot(df$deepspeech_transcription_cleaned_postFeature_WER)
plot(df$google_transcription_cleaned_preFeature_WER)
plot(df$google_transcription_cleaned_postFeature_WER)
plot(df$IBMWatson_transcription_cleaned_preFeature_WER)
plot(df$IBMWatson_transcription_cleaned_postFeature_WER)
plot(df$microsoft_transcription_cleaned_preFeature_WER)
plot(df$microsoft_transcription_cleaned_postFeature_WER)




```



Prepare your variables for regression

```{r}
# Sum coding for feature-type
# contrasts(df$done_type)
df$done_type_factor = as.character(df$Completive)
df$done_type_factor[df$done_type_factor=='0'] <- 'Non-Completive'
df$done_type_factor[df$done_type_factor=='1'] <- 'Completive'
table(df$done_type_factor)
df$done_type_factor = as.factor(df$done_type_factor)
contrasts(df$done_type_factor)
df$done_type_factor <- relevel(df$done_type_factor, ref = 'Non-Completive')
table(df$done_type_factor)
contrasts(df$done_type_factor)
coding = matrix(c(-0.5,0.5))
colnames(coding) = 'Completive.vs.Non-Completive'
coding
contrasts(df$done_type_factor) <- coding
contrasts(df$done_type_factor)


log10.z.vars = c('Content_cleaned_WordCount','Content_cleaned_PreFeature_WordCount','Content_cleaned_PostFeature_WordCount')

z.vars = c(
           'amazon_transcription_cleaned_TotalWER','amazon_transcription_cleaned_preFeature_WER',
           'amazon_transcription_cleaned_postFeature_WER',
           'deepspeech_transcription_cleaned_TotalWER','deepspeech_transcription_cleaned_preFeature_WER',
           'deepspeech_transcription_cleaned_postFeature_WER',
           'google_transcription_cleaned_TotalWER','google_transcription_cleaned_preFeature_WER',
           'google_transcription_cleaned_postFeature_WER',
           'IBMWatson_transcription_cleaned_TotalWER','IBMWatson_transcription_cleaned_preFeature_WER',
           'IBMWatson_transcription_cleaned_postFeature_WER',
           'microsoft_transcription_cleaned_TotalWER','microsoft_transcription_cleaned_preFeature_WER',
           'microsoft_transcription_cleaned_postFeature_WER',
           'SpeechRate', 'WadaSNRRigal'
           )
df = z.fun(df,z.vars)
df = log10.lpc.z.fun(df,log10.z.vars)

df$amazon_transcription_cleaned_correctness = as.factor(df$amazon_transcription_cleaned_correctness)
df$deepspeech_transcription_cleaned_correctness = as.factor(df$deepspeech_transcription_cleaned_correctness)
df$google_transcription_cleaned_correctness = as.factor(df$google_transcription_cleaned_correctness)
df$IBMWatson_transcription_cleaned_correctness = as.factor(df$IBMWatson_transcription_cleaned_correctness)
df$microsoft_transcription_cleaned_correctness = as.factor(df$microsoft_transcription_cleaned_correctness)


df$amazon_correct_factor = df$amazon_transcription_cleaned_correctness
df$deepspeech_correct_factor = df$deepspeech_transcription_cleaned_correctness
df$google_correct_factor = df$google_transcription_cleaned_correctness
df$IBMWatson_correct_factor = df$IBMWatson_transcription_cleaned_correctness
df$microsoft_correct_factor = df$microsoft_transcription_cleaned_correctness



# Sum coding correctness
coding = matrix(c(-0.5,0.5))
colnames(coding) = 'Correct.vs.Incorrect'
coding

contrasts(df$amazon_correct_factor) <- coding
contrasts(df$amazon_correct_factor)

contrasts(df$deepspeech_correct_factor) <- coding
contrasts(df$deepspeech_correct_factor)

contrasts(df$google_correct_factor) <- coding
contrasts(df$google_correct_factor)

contrasts(df$IBMWatson_correct_factor) <- coding
contrasts(df$IBMWatson_correct_factor)

contrasts(df$microsoft_correct_factor) <- coding
contrasts(df$microsoft_correct_factor)

```


# descriptive stats for WER

```{r}
completive.df = subset(df,done_type_factor == 'Completive')
noncompletive.df = subset(df,done_type_factor == 'Non-Completive')


# utterance, amazon pre-feature Non-Completive
errCt = sum(noncompletive.df$amazon_transcription_cleaned_preFeature_errorCount[!is.na(noncompletive.df$amazon_transcription_cleaned_preFeature_errorCount)])
wc = sum(noncompletive.df$Content_cleaned_PreFeature_WordCount)
noncompletive_amazon_preDone_WER = errCt/wc

# utterance, amazon pre-feature Completive
errCt = sum(completive.df$amazon_transcription_cleaned_preFeature_errorCount[!is.na(completive.df$amazon_transcription_cleaned_preFeature_errorCount)])
wc = sum(completive.df$Content_cleaned_PreFeature_WordCount)
completive_amazon_preDone_WER = errCt/wc

noncompletive_amazon_preDone_WER
completive_amazon_preDone_WER
completive_amazon_preDone_WER/noncompletive_amazon_preDone_WER

# utterance, amazon post-feature Non-Completive
errCt = sum(noncompletive.df$amazon_transcription_cleaned_postFeature_errorCount[!is.na(noncompletive.df$amazon_transcription_cleaned_postFeature_errorCount)])
wc = sum(noncompletive.df$Content_cleaned_PostFeature_WordCount)
noncompletive_amazon_postDone_WER = errCt/wc

# utterance, amazon post-feature Completive
errCt = sum(completive.df$amazon_transcription_cleaned_postFeature_errorCount[!is.na(completive.df$amazon_transcription_cleaned_postFeature_errorCount)])
wc = sum(completive.df$Content_cleaned_PostFeature_WordCount)
completive_amazon_postDone_WER = errCt/wc

noncompletive_amazon_postDone_WER
completive_amazon_postDone_WER
completive_amazon_postDone_WER/noncompletive_amazon_postDone_WER




# utterance, deepspeech pre-feature Non-Completive
errCt = sum(noncompletive.df$deepspeech_transcription_cleaned_preFeature_errorCount[!is.na(noncompletive.df$deepspeech_transcription_cleaned_preFeature_errorCount)])
wc = sum(noncompletive.df$Content_cleaned_PreFeature_WordCount)
noncompletive_deepspeech_preDone_WER = errCt/wc

# utterance, deepspeech pre-feature Completive
errCt = sum(completive.df$deepspeech_transcription_cleaned_preFeature_errorCount[!is.na(completive.df$deepspeech_transcription_cleaned_preFeature_errorCount)])
wc = sum(completive.df$Content_cleaned_PreFeature_WordCount)
completive_deepspeech_preDone_WER = errCt/wc

noncompletive_deepspeech_preDone_WER
completive_deepspeech_preDone_WER
completive_deepspeech_preDone_WER/noncompletive_deepspeech_preDone_WER

# utterance, deepspeech post-feature Non-Completive
errCt = sum(noncompletive.df$deepspeech_transcription_cleaned_postFeature_errorCount[!is.na(noncompletive.df$deepspeech_transcription_cleaned_postFeature_errorCount)])
wc = sum(noncompletive.df$Content_cleaned_PostFeature_WordCount)
noncompletive_deepspeech_postDone_WER = errCt/wc

# utterance, deepspeech post-feature Completive
errCt = sum(completive.df$deepspeech_transcription_cleaned_postFeature_errorCount[!is.na(completive.df$deepspeech_transcription_cleaned_postFeature_errorCount)])
wc = sum(completive.df$Content_cleaned_PostFeature_WordCount)
completive_deepspeech_postDone_WER = errCt/wc

noncompletive_deepspeech_postDone_WER
completive_deepspeech_postDone_WER
completive_deepspeech_postDone_WER/noncompletive_deepspeech_postDone_WER




# utterance, google pre-feature Non-Completive
errCt = sum(noncompletive.df$google_transcription_cleaned_preFeature_errorCount[!is.na(noncompletive.df$google_transcription_cleaned_preFeature_errorCount)])
wc = sum(noncompletive.df$Content_cleaned_PreFeature_WordCount)
noncompletive_google_preDone_WER = errCt/wc

# utterance, google pre-feature Completive
errCt = sum(completive.df$google_transcription_cleaned_preFeature_errorCount[!is.na(completive.df$google_transcription_cleaned_preFeature_errorCount)])
wc = sum(completive.df$Content_cleaned_PreFeature_WordCount)
completive_google_preDone_WER = errCt/wc

noncompletive_google_preDone_WER
completive_google_preDone_WER
completive_google_preDone_WER/noncompletive_google_preDone_WER

# utterance, google post-feature Non-Completive
errCt = sum(noncompletive.df$google_transcription_cleaned_postFeature_errorCount[!is.na(noncompletive.df$google_transcription_cleaned_postFeature_errorCount)])
wc = sum(noncompletive.df$Content_cleaned_PostFeature_WordCount)
noncompletive_google_postDone_WER = errCt/wc

# utterance, google post-feature Completive
errCt = sum(completive.df$google_transcription_cleaned_postFeature_errorCount[!is.na(completive.df$google_transcription_cleaned_postFeature_errorCount)])
wc = sum(completive.df$Content_cleaned_PostFeature_WordCount)
completive_google_postDone_WER = errCt/wc

noncompletive_google_postDone_WER
completive_google_postDone_WER
completive_google_postDone_WER/noncompletive_google_postDone_WER




# utterance, IBMWatson pre-feature Non-Completive
errCt = sum(noncompletive.df$IBMWatson_transcription_cleaned_preFeature_errorCount[!is.na(noncompletive.df$IBMWatson_transcription_cleaned_preFeature_errorCount)])
wc = sum(noncompletive.df$Content_cleaned_PreFeature_WordCount)
noncompletive_IBMWatson_preDone_WER = errCt/wc

# utterance, IBMWatson pre-feature Completive
errCt = sum(completive.df$IBMWatson_transcription_cleaned_preFeature_errorCount[!is.na(completive.df$IBMWatson_transcription_cleaned_preFeature_errorCount)])
wc = sum(completive.df$Content_cleaned_PreFeature_WordCount)
completive_IBMWatson_preDone_WER = errCt/wc

noncompletive_IBMWatson_preDone_WER
completive_IBMWatson_preDone_WER
completive_IBMWatson_preDone_WER/noncompletive_IBMWatson_preDone_WER

# utterance, IBMWatson post-feature Non-Completive
errCt = sum(noncompletive.df$IBMWatson_transcription_cleaned_postFeature_errorCount[!is.na(noncompletive.df$IBMWatson_transcription_cleaned_postFeature_errorCount)])
wc = sum(noncompletive.df$Content_cleaned_PostFeature_WordCount)
noncompletive_IBMWatson_postDone_WER = errCt/wc

# utterance, IBMWatson post-feature Completive
errCt = sum(completive.df$IBMWatson_transcription_cleaned_postFeature_errorCount[!is.na(completive.df$IBMWatson_transcription_cleaned_postFeature_errorCount)])
wc = sum(completive.df$Content_cleaned_PostFeature_WordCount)
completive_IBMWatson_postDone_WER = errCt/wc

noncompletive_IBMWatson_postDone_WER
completive_IBMWatson_postDone_WER
completive_IBMWatson_postDone_WER/noncompletive_IBMWatson_postDone_WER



# utterance, microsoft pre-feature Non-Completive
errCt = sum(noncompletive.df$microsoft_transcription_cleaned_preFeature_errorCount[!is.na(noncompletive.df$microsoft_transcription_cleaned_preFeature_errorCount)])
wc = sum(noncompletive.df$Content_cleaned_PreFeature_WordCount)
noncompletive_microsoft_preDone_WER = errCt/wc

# utterance, microsoft pre-feature Completive
errCt = sum(completive.df$microsoft_transcription_cleaned_preFeature_errorCount[!is.na(completive.df$microsoft_transcription_cleaned_preFeature_errorCount)])
wc = sum(completive.df$Content_cleaned_PreFeature_WordCount)
completive_microsoft_preDone_WER = errCt/wc

noncompletive_microsoft_preDone_WER
completive_microsoft_preDone_WER
completive_microsoft_preDone_WER/noncompletive_microsoft_preDone_WER

# utterance, microsoft post-feature Non-Completive
errCt = sum(noncompletive.df$microsoft_transcription_cleaned_postFeature_errorCount[!is.na(noncompletive.df$microsoft_transcription_cleaned_postFeature_errorCount)])
wc = sum(noncompletive.df$Content_cleaned_PostFeature_WordCount)
noncompletive_microsoft_postDone_WER = errCt/wc

# utterance, microsoft post-feature Completive
errCt = sum(completive.df$microsoft_transcription_cleaned_postFeature_errorCount[!is.na(completive.df$microsoft_transcription_cleaned_postFeature_errorCount)])
wc = sum(completive.df$Content_cleaned_PostFeature_WordCount)
completive_microsoft_postDone_WER = errCt/wc

noncompletive_microsoft_postDone_WER
completive_microsoft_postDone_WER
completive_microsoft_postDone_WER/noncompletive_microsoft_postDone_WER


```

# Analysis 1: Predicting Correctness by Feature Type 

while controlling for
* Speech Rate,
* Speech-to-Noise Ratio (WADA), 
* Pre-Feature Word Count, Post-Feature Word Count
* Pre-Feature Word Error Rate, Post-Feature Word Error Rate



## Amazon

```{r}
# Amazon


amazon.utt.utt_prepost.wc_WER_sr_snr_glmermod = glmer(amazon_transcription_cleaned_correctness ~  
                    done_type_factor +
                    Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    amazon_transcription_cleaned_preFeature_WER.z +
                    Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    amazon_transcription_cleaned_postFeature_WER.z + 
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1 |Speaker)
                      , data=df,family=binomial, control=glmerControl(optimizer="bobyqa"))
summary(amazon.utt.utt_prepost.wc_WER_sr_snr_glmermod)
plot_model(amazon.utt.utt_prepost.wc_WER_sr_snr_glmermod, type = "est")


```



## deepspeech

```{r}
# deepspeech


deepspeech.utt.utt_prepost.wc_WER_sr_snr_glmermod = glmer(deepspeech_transcription_cleaned_correctness ~  
                    #done_type_factor +
                    Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    deepspeech_transcription_cleaned_preFeature_WER.z +
                    Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    deepspeech_transcription_cleaned_postFeature_WER.z + 
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1 |Speaker)
                      , data=df,family=binomial, control=glmerControl(optimizer="Nelder_Mead"))
summary(deepspeech.utt.utt_prepost.wc_WER_sr_snr_glmermod)
plot_model(deepspeech.utt.utt_prepost.wc_WER_sr_snr_glmermod, type = "est")


```



## google

```{r}
# google


google.utt.utt_prepost.wc_WER_sr_snr_glmermod = glmer(google_transcription_cleaned_correctness ~  
                    done_type_factor +
                    Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    google_transcription_cleaned_preFeature_WER.z +
                    Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    google_transcription_cleaned_postFeature_WER.z + 
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1 |Speaker)
                      , data=df,family=binomial, control=glmerControl(optimizer="bobyqa"))
summary(google.utt.utt_prepost.wc_WER_sr_snr_glmermod)
plot_model(google.utt.utt_prepost.wc_WER_sr_snr_glmermod, type = "est")


```



## IBMWatson

```{r}
# IBMWatson


IBMWatson.utt.utt_prepost.wc_WER_sr_snr_glmermod = glmer(IBMWatson_transcription_cleaned_correctness ~  
                    done_type_factor +
                    Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    IBMWatson_transcription_cleaned_preFeature_WER.z +
                    Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    IBMWatson_transcription_cleaned_postFeature_WER.z + 
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1 |Speaker)
                      , data=df,family=binomial, control=glmerControl(optimizer="bobyqa"))
summary(IBMWatson.utt.utt_prepost.wc_WER_sr_snr_glmermod)
plot_model(IBMWatson.utt.utt_prepost.wc_WER_sr_snr_glmermod, type = "est")


```


## microsoft

```{r}
# microsoft


microsoft.utt.utt_prepost.wc_WER_sr_snr_glmermod = glmer(microsoft_transcription_cleaned_correctness ~  
                    done_type_factor +
                    Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    microsoft_transcription_cleaned_preFeature_WER.z +
                    Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    microsoft_transcription_cleaned_postFeature_WER.z + 
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1 |Speaker)
                      , data=df,family=binomial, control=glmerControl(optimizer="bobyqa"))
summary(microsoft.utt.utt_prepost.wc_WER_sr_snr_glmermod)
plot_model(microsoft.utt.utt_prepost.wc_WER_sr_snr_glmermod, type = "est")


```







# Analysis 2: Estimating Surrounding Word Error Rate with Feature Type

while controlling for
* Feature Correctness
* Speech Rate
* Speech-to-Noise Rate (WADA)

specifically:
* Post-Feature Word Count for the Word Error Rate of the Pre-Feature Word Count
* Post-Feature Word Error Rate for the Word Error Rate of the Pre-Feature Word Error Rate

## Amazon: Pre-Feature

```{r}
amazon.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod = lmerTest::lmer(amazon_transcription_cleaned_preFeature_WER ~
                    done_type_factor +
                    amazon_correct_factor +
                    amazon_transcription_cleaned_postFeature_WER.z + 
                    # Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1|Speaker)
                      , data=df)
summary(amazon.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod,ddf = "Satterthwaite")
plot_model(amazon.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod, type = "est")
```

## Amazon: Post-Feature

```{r}
amazon.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod = lmerTest::lmer(amazon_transcription_cleaned_postFeature_WER ~
                    done_type_factor +                                                              
                    amazon_correct_factor +
                    amazon_transcription_cleaned_preFeature_WER.z + 
                    Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    # Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1|Speaker)
                      , data=df)
summary(amazon.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod,ddf = "Satterthwaite")
plot_model(amazon.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod, type = "est")
```



## deepspeech: Pre-Feature

```{r}
deepspeech.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod = lmerTest::lmer(deepspeech_transcription_cleaned_preFeature_WER ~
                    done_type_factor +
                    deepspeech_correct_factor +
                    deepspeech_transcription_cleaned_postFeature_WER.z + 
                    # Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1|Speaker)
                      , data=df)
summary(deepspeech.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod,ddf = "Satterthwaite")
plot_model(deepspeech.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod, type = "est")
```

## deepspeech: Post-Feature

```{r}
deepspeech.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod = lmerTest::lmer(deepspeech_transcription_cleaned_postFeature_WER ~
                    done_type_factor +                                                              
                    deepspeech_correct_factor +
                    deepspeech_transcription_cleaned_preFeature_WER.z + 
                    Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    # Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1|Speaker)
                      , data=df)
summary(deepspeech.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod,ddf = "Satterthwaite")
plot_model(deepspeech.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod, type = "est")
```



## google: Pre-Feature

```{r}
google.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod = lmerTest::lmer(google_transcription_cleaned_preFeature_WER ~
                    done_type_factor +
                    google_correct_factor +
                    google_transcription_cleaned_postFeature_WER.z + 
                    # Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1|Speaker)
                      , data=df)
summary(google.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod,ddf = "Satterthwaite")
plot_model(google.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod, type = "est")
```

## google: Post-Feature

```{r}
google.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod = lmerTest::lmer(google_transcription_cleaned_postFeature_WER ~
                    done_type_factor +                                                              
                    google_correct_factor +
                    google_transcription_cleaned_preFeature_WER.z + 
                    Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    # Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1|Speaker)
                      , data=df)
summary(google.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod,ddf = "Satterthwaite")
plot_model(google.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod, type = "est")
```




## IBMWatson: Pre-Feature

```{r}
IBMWatson.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod = lmerTest::lmer(IBMWatson_transcription_cleaned_preFeature_WER ~
                    done_type_factor +
                    IBMWatson_correct_factor +
                    IBMWatson_transcription_cleaned_postFeature_WER.z + 
                    # Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1|Speaker)
                      , data=df)
summary(IBMWatson.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod,ddf = "Satterthwaite")
plot_model(IBMWatson.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod, type = "est")
```

## IBMWatson: Post-Feature

```{r}
IBMWatson.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod = lmerTest::lmer(IBMWatson_transcription_cleaned_postFeature_WER ~
                    done_type_factor +                                                              
                    IBMWatson_correct_factor +
                    IBMWatson_transcription_cleaned_preFeature_WER.z + 
                    Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    # Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1|Speaker)
                      , data=df)
summary(IBMWatson.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod,ddf = "Satterthwaite")
plot_model(IBMWatson.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod, type = "est")
```



## microsoft: Pre-Feature

```{r}
microsoft.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod = lmerTest::lmer(microsoft_transcription_cleaned_preFeature_WER ~
                    done_type_factor +
                    microsoft_correct_factor +
                    microsoft_transcription_cleaned_postFeature_WER.z + 
                    # Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1|Speaker)
                      , data=df)
summary(microsoft.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod,ddf = "Satterthwaite")
plot_model(microsoft.utt.utt_preWER_prepost.cor.wc_WER_sr_snr.lmermod, type = "est")
```

## microsoft: Post-Feature

```{r}
microsoft.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod = lmerTest::lmer(microsoft_transcription_cleaned_postFeature_WER ~
                    done_type_factor +                                                              
                    microsoft_correct_factor +
                    microsoft_transcription_cleaned_preFeature_WER.z + 
                    Content_cleaned_PreFeature_WordCount.log10.lpc.z +
                    # Content_cleaned_PostFeature_WordCount.log10.lpc.z +
                    SpeechRate.z +
                    WadaSNRRigal.z +
                    (1|Speaker)
                      , data=df)
summary(microsoft.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod,ddf = "Satterthwaite")
plot_model(microsoft.utt.utt_postWER_prepost.cor.wc_WER_sr_snr.lmermod, type = "est")
```




